Forecasting the United States 2024 Presidential Election

### 2024-11-04 paper/paper.qmd
fixed

---
title: "Forecasting the United States 2024 Presidential Election"
subtitle: "Kamala Harris wins 60th presidency with 265 Electoral College Votes"
author: 
  - Robert Ford
  - Michelle Ji
  - Cher Ning
thanks: "Code and data are available at: https://github.com/Ford-Robert/us-presidential-election."
date: today
date-format: long
abstract: "This report analyzes compiled polling surveys for the 2024 U.S. presidential election using FiveThirtyEight data [@538data] and the 'pool of polls' method. From the analysis, bayesian and generalized linear models were built to forecast the outcome of the presidential election based on popular vote and the electoral college system. The models forecast Kamala Harris as the winner of election, winning 265 electoral college votes versus the 172 votes Donald Trump acquires. Election forecasting is crucial for informing voters, guiding campaign strategies, and engaging the public in the electoral process. Additionally, it helps predict potential policy shifts and holds political institutions accountable, contributing to a more transparent and informed democracy."
format: pdf
header-includes:
  - \usepackage{geometry}
  - \geometry{margin=0.75in} 
number-sections: true
bibliography: references.bib
---
![State Election Predictions](other/plots/election_map.png){width=80%}

>>>>

---
title: "Forecasting the United States 2024 Presidential Election"
subtitle: "Kamala Harris wins 60th presidency with 265 Electoral College Votes"
author: 
  - Robert Ford
  - Michelle Ji
  - Cher Ning
thanks: "Code and data are available at: https://github.com/Ford-Robert/us-presidential-election."
date: today
date-format: long
abstract: "This report analyzes compiled polling surveys for the 2024 U.S. presidential election using FiveThirtyEight data [@538data] and the 'pool of polls' method. From the analysis, bayesian and generalized linear models were built to forecast the outcome of the presidential election based on popular vote and the electoral college system. The models forecast Kamala Harris as the winner of election, winning 265 electoral college votes versus the 172 votes Donald Trump acquires. Election forecasting is crucial for informing voters, guiding campaign strategies, and engaging the public in the electoral process. Additionally, it helps predict potential policy shifts and holds political institutions accountable, contributing to a more transparent and informed democracy."
format: pdf
header-includes:
  - \usepackage{geometry}
  - \geometry{margin=0.75in} 
number-sections: true
bibliography: references.bib
---
